---
title: "Keyword Search: Comparing Narrow vs. Extended Keywords"
author: "Maria Antonia Bravo"
date: '2022-06-09'
output: html_document
---

```{r}
# For data wrangling
library("tidyverse")
library("lubridate")
library("readxl")
# For text analysis
library("pdftools")
library("stringr")
library("quanteda")
library("readtext")

# For SQL
library(DBI)
library(RSQLite)
Sys.setenv(LANG = "en")
```

#Loading in the Data from SQL

```{r}
db <- dbConnect(RSQLite::SQLite(), "news_data.sqlite")

# CHAD
## Narrow Search
### Q:(cris* or disaster*) and (humanitarian) and (chad)
### T: January 1, 2017 - July 1, 2017
### S: All articles

chad_narrow_all <- dbGetQuery(db, "SELECT * FROM chad_narrow_firsthalf_2017_all")

### Q&T (Above)
### S: First 500 - Relevance
chad_narrow_rel <- dbGetQuery(db, "SELECT * FROM chad_narrow_firsthalf_2017_relevance")

## Extended Search
### Q: (cris* or disaster or food or refuge* or aid or assistance or response or war or border) and (humanitarian) and (chad)
### T: January 1, 2017 - July 1, 2017
### S: All articles
chad_extended_all <- dbGetQuery(db, "SELECT * FROM chad_extended_firsthalf_2017_all")
  
### Q&T (Above)
### S: First 500 - Relevance
chad_extended_rel <- dbGetQuery(db, "SELECT * FROM chad_extended_firsthalf_2017_relevance")
  
# GENERAL NEWS (i.e, not bounded by Country)
## Narrow Search
### Q: (cris* or disaster*) and (humanitarian)
### T: January 1, 2017 - July 1 (500), 2017 & July 2, 20 (500)
### S: First 500 - Relevance (from both time frames)
narrow_rel <- dbGetQuery(db, "SELECT * FROM narrow_2017_relevance")

## Extended Search
## Q:(cris* or disaster or food or refuge* or aid or assistance or response or war or border) and humanitarian
extended_rel <- dbGetQuery(db, "SELECT * FROM extended_2017_relevance")
```

# General Search
Summary Statistics from Articles
```{r warning=FALSE}
list_dfs_gensearch <- list(narrow_rel, extended_rel)
list_names_gensearch <- c("Narrow Search (2017) - Rel 500", "Extended Search (2017) - Rel 500")
for (ref in 1:length(list_dfs_gensearch)){
  
  # Number of articles
  flush.console()
  total = nrow(list_dfs_gensearch[[ref]])
  print(sprintf("'%s' search contains %g articles in total",
                       list_names_gensearch[ref], total))
  
  # Number of duplicate headlines
  dup_head = nrow(list_dfs_gensearch[[ref]]) - length(unique(list_dfs_gensearch[[ref]]$headline))
  print(sprintf("Articles in '%s' search contain %g duplicate articles, roughly %g percent.",
                       list_names_gensearch[ref], dup_head, round(dup_head/total*100, 2)))
    
  
  # Number of repeated articles
  num_rep = nrow(list_dfs_gensearch[[ref]] %>%
                       group_by(headline) %>%
                       summarise(count = n()) %>%
                       filter(count > 1))
  print(sprintf("Articles in '%s' search contain %g unique duplicate articles, roughly %g percent.",
                list_names_gensearch[ref], num_rep, round(num_rep/total*100, 2)))
  
  # Most repeated article 
  rep_arts <- list_dfs_gensearch[[ref]][grep((list_dfs_gensearch[[ref]] %>%
    group_by(headline) %>%
    summarise(count = n()) %>%
    filter(count == max(count)))$headline, list_dfs_gensearch[[ref]]$headline),]
  
  print(sprintf("The most repeated article in '%s' search is '%s' published %g times around %s by %g sources", 
                list_names_gensearch[ref], rep_arts[1,3], nrow(rep_arts), rep_arts[1,5],
                length(unique(rep_arts$source))))
  
  # Showing the number of articles published by source
  print(head(list_dfs_gensearch[[ref]] %>% 
    group_by(source) %>% 
    summarise(count = n()) %>%
    arrange(desc(count))))
  
  # Showing the number of articles published per copy right (head)
  print(head(list_dfs_gensearch[[ref]] %>% 
    group_by(copyright) %>% 
    summarise(count = n()) %>%
    arrange(desc(count)))
  )
}

```

# Chad Case Study
Summary Statistics from Articles
```{r warning=FALSE}
list_dfs <- list(chad_extended_all, chad_extended_rel, chad_narrow_all, chad_narrow_rel)
list_names <- c("Chad Extended - All", "Chad Extended - First Rel 500", "Chad Narrow - All", "Chad Narrow - First Rel 500")

for (ref in 1:length(list_dfs)){
  
  # Number of articles
  flush.console()
  total = nrow(list_dfs[[ref]])
  print(sprintf("'%s' search contains %g articles in total",
                       list_names[ref], total))
  
  # Number of duplicate headlines
  dup_head = nrow(list_dfs[[ref]]) - length(unique(list_dfs[[ref]]$headline))
  print(sprintf("Articles in '%s' search contain %g duplicate articles, roughly %g percent.",
                       list_names[ref], dup_head, round(dup_head/total*100, 2)))
    
  
  # Number of repeated articles
  num_rep = nrow(list_dfs[[ref]] %>%
                       group_by(headline) %>%
                       summarise(count = n()) %>%
                       filter(count > 1))
  print(sprintf("Articles in '%s' search contain %g unique duplicate articles, roughly %g percent.",
                list_names[ref], num_rep, round(num_rep/total*100, 2)))
  
  # Most repeated article 
  rep_arts <- list_dfs[[ref]][grep((list_dfs[[ref]] %>%
    group_by(headline) %>%
    summarise(count = n()) %>%
    filter(count == max(count)))$headline, list_dfs[[ref]]$headline),]
  
  print(sprintf("The most repeated article in '%s' search is '%s' published %g times around %s by %g sources", 
                list_names[ref], rep_arts[1,3], nrow(rep_arts), rep_arts[1,5],
                length(unique(rep_arts$source))))
  
  # Showing the number of articles published by source
  print(head(list_dfs[[ref]] %>% 
    group_by(source) %>% 
    summarise(count = n()) %>%
    arrange(desc(count))))
  
  # Showing the number of articles published per copy right (head)
  print(head(list_dfs[[ref]] %>% 
    group_by(copyright) %>% 
    summarise(count = n()) %>%
    arrange(desc(count)))
  )
}

#"Chad Extended - All", "Chad Extended - First Rel 500", "Chad Narrow - All", "Chad Narrow - First Rel 500"
```

```{r}
for (ref in 1:length(list_dfs)){
  # Formatting date
  list_dfs[[ref]]$date_formatted <- as.Date(list_dfs[[ref]]$date_formatted, origin =
                                              lubridate::origin)
  
  list_dfs[[ref]]$weeks <- week(list_dfs[[ref]]$date_formatted)
  list_dfs[[ref]]$year <- year(list_dfs[[ref]]$date_formatted)
  
  # Plotting weekly counts
  list_dfs[[ref]]$weeks <- cut(list_dfs[[ref]][,"date_formatted"], breaks="week")
  agg <- list_dfs[[ref]] %>% group_by(weeks) %>% summarise(count = n())
  agg <- agg[1:nrow(agg)-1, ]
  
  g <- ggplot(agg, aes(x = as.Date(weeks), y = count)) +
    geom_point() +
    scale_x_date(date_breaks = "months" , date_labels = "%b-%y") +
    ylab("# of Articles") + 
    xlab("Week") + 
    labs(title = sprintf("%s", list_names[ref])) + 
    geom_line() + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
  
  print(g)
}
```
```{r}
#"Chad Extended - All", "Chad Extended - First Rel 500", "Chad Narrow - All", "Chad Narrow - First Rel 500"
#list_dfs <- list(chad_extended_all, chad_extended_rel, chad_narrow_all, chad_narrow_rel)
#list_names <- c("Chad Extended - All", "Chad Extended - First Rel 500", "Chad Narrow - All", "Chad Narrow - First Rel 500")

# Chad Extended vs. Chad Narrow
## Plotting weekly counts 
  colors = c("Narrow Search (All)" = "dark blue", "Extended Search (All)" = "dark red")
  

  agg_extended <- list_dfs[[1]] %>% group_by(weeks) %>% summarise(count = n())
  agg_extended <- agg_extended[1:nrow(agg_extended)-1, ]
  agg_narrow <- list_dfs[[3]] %>% group_by(weeks) %>% summarise(count = n())
  agg_narrow <- agg_narrow[1:nrow(agg_narrow)-1, ]

  g <- ggplot(NULL, aes(x = as.Date(weeks), y = count)) +
    geom_line(data = agg_extended,
              aes(
                x = as.Date(weeks),
                y = count,
                color = "Extended Search (All)"
              )) +
    geom_line(data = agg_narrow, aes(
      x = as.Date(weeks),
      y = count,
      color = "Narrow Search (All)"
    )) +
    scale_x_date(date_breaks = "months" , date_labels = "%b-%Y") +
    labs(
      title = "Chad Case Study:Number of Articles per Week",
      x = "Date",
      y = "Number of Articles (Weekly Counts)",
      color = "Legend"
    ) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
    scale_color_manual(values = colors)
    
  g
```
```{r}
# Chad Extended vs. Chad Narrow (Relevance)
## Plotting weekly counts 

  agg_extended_rel <- list_dfs[[2]] %>% group_by(weeks) %>% summarise(count = n())
  agg_extended_rel <- agg_extended_rel[1:nrow(agg_extended_rel)-1, ]
  agg_narrow_rel <- list_dfs[[4]] %>% group_by(weeks) %>% summarise(count = n())
  agg_narrow_rel <- agg_narrow_rel[1:nrow(agg_narrow_rel)-1, ]
  colors = c("Narrow Search (Rel)" = "blue", "Extended Search (Rel)" = "red")

  f <- ggplot(NULL, aes(x = as.Date(weeks), y = count)) +
    geom_line(data = agg_extended_rel,
              aes(
                x = as.Date(weeks),
                y = count,
                color = "Extended Search (Rel)"
              )) +
    geom_line(data = agg_narrow_rel, aes(
      x = as.Date(weeks),
      y = count,
      color = "Narrow Search (Rel)"
    )) +
    scale_x_date(date_breaks = "months" , date_labels = "%b-%Y") +
    labs(
      title = "Chad Case Study:Number of Articles per Week (Relevance)",
      x = "Date",
      y = "Number of Articles (Weekly Counts)",
      color = "Legend"
    ) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
    scale_color_manual(values = colors)
    
  f

```
```{r}
colors = c("Narrow Search (All)" = "dark blue", "Extended Search (All)" = "dark red", "Narrow Search (Rel)" = "blue", "Extended Search (Rel)" = "red")

a <- ggplot(NULL) +
    geom_line(data = agg_extended,
              aes(
                x = as.Date(weeks),
                y = count,
                color = "Extended Search (All)"
              )) +
    geom_line(data = agg_narrow, aes(
      x = as.Date(weeks),
      y = count,
      color = "Narrow Search (All)"
    )) +
  geom_line(data = agg_extended_rel, aes(
      x = as.Date(weeks),
      y = count,
      color = "Extended Search (Rel)"
    )) +
    geom_line(data = agg_narrow_rel, aes(
      x = as.Date(weeks),
      y = count,
      color = "Narrow Search (Rel)"
    )) + 
    scale_x_date(date_breaks = "months" , date_labels = "%b-%Y") +
    labs(
      title = "Chad Case Study:Number of Articles per Week (Relevance)",
      x = "Date",
      y = "Number of Articles (Weekly Counts)",
      color = "Legend"
    ) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
    scale_color_manual(values = colors)
    
a
```

It appears that queries based on relevance mimic the distribution of the overall articles (even if these are supposed to capture the hits with greatest relevance within a time period). This suggests that non-relevant articles (per LexisNexis algorithm) are weeded out from the top hits. The shape of the lines follow the same pattern across the query methods, notably rising and falling around the same weeks. This suggests that similar events are being covered across. 

```{r}
# list_dfs_gensearch <- list(narrow_rel, extended_rel)
# list_names_gensearch <- c("Narrow Search (2017) - Rel 500", "Extended Search (2017) - Rel 500")

for (ref in 1:length(list_dfs_gensearch)){
  # Formatting date
  list_dfs_gensearch[[ref]]$date_formatted <- as.Date(list_dfs_gensearch[[ref]]$date_formatted, origin =
                                              lubridate::origin)
  
  list_dfs_gensearch[[ref]]$weeks <- week(list_dfs_gensearch[[ref]]$date_formatted)
  list_dfs_gensearch[[ref]]$year <- year(list_dfs_gensearch[[ref]]$date_formatted)
  
  # Plotting weekly counts
  list_dfs_gensearch[[ref]]$weeks <- cut(list_dfs_gensearch[[ref]][,"date_formatted"], breaks="week")
  agg <- list_dfs_gensearch[[ref]] %>% group_by(weeks) %>% summarise(count = n())
  agg <- agg[1:nrow(agg)-1, ]
  
  g <- ggplot(agg, aes(x = as.Date(weeks), y = count)) +
    geom_point() +
    scale_x_date(date_breaks = "years" , date_labels = "%b-%y") +
    ylab("Aggregated by Week") + 
    xlab("Week") + 
    labs(title = sprintf("%s", list_names_gensearch[ref])) + 
    geom_line() + 
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
  
  print(g)
}

# General
## Plotting weekly counts 
  
  agg_extended_genrel <- list_dfs_gensearch[[2]] %>% group_by(weeks) %>% summarise(count = n())
  agg_extended_genrel <- agg_extended_genrel[1:nrow(agg_extended_genrel)-1, ]
  agg_narrow_genrel <- list_dfs_gensearch[[1]] %>% group_by(weeks) %>% summarise(count = n())
  agg_narrow_genrel <- agg_narrow_genrel[1:nrow(agg_narrow_genrel)-1, ]
  colors = c("Narrow Search" = "blue", "Extended Search" = "red")

  f <- ggplot(NULL, aes(x = as.Date(weeks), y = count)) +
    geom_line(data = agg_extended_genrel,
              aes(
                x = as.Date(weeks),
                y = count,
                color = "Extended Search"
              )) +
    geom_line(data = agg_narrow_genrel, aes(
      x = as.Date(weeks),
      y = count,
      color = "Narrow Search"
    )) +
    scale_x_date(date_breaks = "months" , date_labels = "%b-%Y") +
    labs(
      title = "Number of Articles per Week (Relevance)",
      x = "Date",
      y = "Number of Articles (Weekly Counts)",
      color = "Legend"
    ) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
    scale_color_manual(values = colors)
    
  f
```

What are the countries mentioned in these articles?
for 2017 - Ethiopia, Somalia, Kenya nad South Sudan, Yemen, Banladesh, Manmar, Chad, Cameeron, Niger and Nigeria, Syria, Democratic Republic of the Congo, Eritrea, Burundi, Central African Republic
```{r}
# Ethiopia: Appears in both. 49 times in Narrow vs. 85 times in Extended. 
find_word <- function(list_of_dfs, df_names, query_field = 'text', 
                      query = c("humanitarian", "congo")) {
  
  saved <- NULL
  saved$query <- query
  saved$df <- df_names[1]
  saved$count <- 0 
  saved <- as.data.frame(saved)
  indx <- 1
  
  for (q in 1:length(query)){
  
    for (li in 1:length(list_of_dfs)) {
    
    if (query_field == 'text')  {
    num_hits = length(grep(query[q], tolower(list_of_dfs[[li]]$text), ignore.case = TRUE))
    (sprintf("%g articles in '%s' contain one or more mentions of the query %s", num_hits, df_names[li], query))
    }
    
    if (query_field == 'headline') {
      num_hits = length(grep(query[q], tolower(list_of_dfs[[li]]$headline), ignore.case = TRUE))
    (sprintf("%g articles in '%s' contain one or more mentions of the query %s", num_hits, df_names[li], query))
    }
      
    saved[indx,1] <- query[q]
    saved[indx, 2] <-  df_names[li]
    saved[indx, 3] <-num_hits
    indx <- indx + 1
  } }
  return(saved)
}

# Conducting queries to check the presence of different keywords
queries <- c("ethiopia", "somalia", "drc", "democratic republic of the congo", "zambia", "burundi", "burkina faso", "bangladesh", "congo", "syria", "central african republic", "caf", "afghanistan")

# Headline
headline_results <- find_word(list_dfs_gensearch, list_names_gensearch, query_field = 'headline', query = queries)
headline_results %>%
  group_by(query) %>%
  mutate(diff=count-lag(count,default=first(count))) %>%
  filter(diff < 0)

# Looking further into the Congo case
extended_congo <- list_dfs_gensearch[[2]][grep("congo", tolower(list_dfs_gensearch[[2]]$headline)),]$headline
narrow_congo <- list_dfs_gensearch[[1]][grep("congo", tolower(list_dfs_gensearch[[1]]$headline)),]$headline

## 1 article in both (given that extended search only contains that one article)
sum(extended_congo %in% narrow_congo)
sum(narrow_congo %in% extended_congo)
extended_congo[extended_congo %in% narrow_congo] # article appears to be relevant

## articles that were collected in the narrow search, not in the extended
narrow_congo[!(narrow_congo %in% extended_congo)]
## from the headline, all articles appear to be relevant

```
```{r}
# Looking further into the DRC case
extended_drc <- list_dfs_gensearch[[2]][grep("drc", tolower(list_dfs_gensearch[[2]]$headline)),]$headline
narrow_drc <- list_dfs_gensearch[[1]][grep("drc", tolower(list_dfs_gensearch[[1]]$headline)),]$headline

## The articlecles in both sets are completely different, there is not overlap
sum(extended_drc %in% narrow_drc)
sum(narrow_drc %in% extended_drc)

## articles that were collected in the narrow search, not in the extended
narrow_drc[!(narrow_drc %in% extended_drc)]

## articles that were collected in the extended search, not in the narrow
extended_drc[!(extended_drc %in% narrow_drc)]
```

```{r warning=FALSE}
find_similarities <- function(list_of_dfs, search_type = "general", query_field = 'text', 
                      query = c("congo", "zambia")) {
  
  ### Only takes two dataframes to compare at at time
  
  saved <- NULL
  saved$query <- 'query'
  saved$df <- "general"
  saved$Total_Articles_Narrow <- 0
  saved$Total_Articles_Extended <- 0 
  saved$Articles_in_Narrow_and_Extended <- 0
  saved$Articles_in_Extended_and_Narrow <- 0
  saved$Exact_Matches <- 0
  saved$Articles_in_Narrow_notin_Extended <- 0
  saved$Articles_in_Extended_notin_Narrow <- 0
  saved <- as.data.frame(saved)
  indx <- 1
  
  for (q in 1:length(query)){
  
    if (query_field == 'text')  {
    narrow_hits = list_of_dfs[[1]][grep(query[q], tolower(list_of_dfs[[1]]$text),
                                        ignore.case = TRUE),]$text
    
    # Returns the indices were the keyword appears
    extended_hits = list_of_dfs[[2]][grep(query[q], tolower(list_of_dfs[[2]]$text),
                                          ignore.case = TRUE),]$text
    }
    
    if (query_field == 'headline') {
    narrow_hits = list_of_dfs[[1]][grep(query[q], tolower(list_of_dfs[[1]]$headline),
                                          ignore.case = TRUE),]$headline

    # Returns the indices were the keyword appears
    extended_hits = list_of_dfs[[2]][grep(query[q], tolower(list_of_dfs[[2]]$headline),
                                          ignore.case = TRUE),]$headline
    }
  
    saved[indx,1] <- query[q]
    saved[indx, 2] <-  search_type
    saved[indx, 3] <- length(narrow_hits)
    saved[indx, 4] <- length(extended_hits)
    saved[indx, 5] <- sum(narrow_hits %in% extended_hits)
    saved[indx, 6] <- sum(extended_hits %in% narrow_hits)
    saved[indx, 7] <- ifelse(FALSE %in% (extended_hits[(extended_hits %in% narrow_hits)] == narrow_hits[(narrow_hits %in% extended_hits)]), 'FALSE', 'TRUE')
    saved[indx, 8] <- sum(!(narrow_hits %in% extended_hits))
    saved[indx, 9] <- sum(!(extended_hits %in% narrow_hits))
    indx <- indx + 1
  } 
  return(saved)
}
queries <- c('humanitarian', 'humanitarian disaster', "ethiopia", "somalia", "drc", "democratic republic of the congo", "zambia", "burundi", "burkina faso", "bangladesh", "congo", "syria", "central african republic", "caf", "afghanistan", "a")


similarities_headline <- find_similarities(list_dfs_gensearch, "n_vs_e_2017_headline", 
                             query_field = 'headline', query = queries)


similarities_text <- find_similarities(list_dfs_gensearch, "n_vs_e_2017_text", 
                             query_field = 'text', query = queries) 

queries <- c('humanitarian', 'humanitarian disaster', "humanitarian assistance", "drought", "famine", "hunger", "boko haram", "poverty", "insurgency", "un", "refugee", "idps", "internally displaced",  "a")

list_chad_rel <- list(chad_extended_rel, chad_narrow_rel)
similarities_text_chad_rel <- find_similarities(list_chad_rel, "chad_rel", 
                             query_field = 'text', query = queries)
similarities_headline_chad_rel <- find_similarities(list_chad_rel, "chad_rel", 
                             query_field = 'text', query = queries)

list_chad_all <- list(chad_extended_all, chad_narrow_all)
similarities_text_chad_all <- find_similarities(list_chad_all, "chad_all", 
                             query_field = 'text', query = queries)
similarities_headline_chad_all <- find_similarities(list_chad_all, "chad_all", 
                             query_field = 'text', query = queries)

list_chad_extended <- list(chad_extended_rel, chad_extended_all)
similarities_text_chad_extended <- find_similarities(list_chad_extended, "chad_ext", 
                             query_field = 'text', query = queries)
similarities_headline_chad_extended <- find_similarities(list_chad_extended, "chad_ext", 
                             query_field = 'text', query = queries)

list_chad_narrow <- list(chad_narrow_rel, chad_narrow_all)
similarities_text_chad_narrow <- find_similarities(list_chad_narrow, "chad_narrow", 
                             query_field = 'text', query = queries)
similarities_headline_chad_narrow <- find_similarities(list_chad_narrow, "chad_narrow", 
                             query_field = 'text', query = queries)

tab_1 <- similarities_text %>%
  select(-df) %>%
  mutate(Share_Articles_in_Narrow_and_Extended = round(Total_Articles_Narrow / Articles_in_Narrow_and_Extended, 2), 
         Share_Articles_in_Extended_and_Narrow = round(Total_Articles_Extended / Articles_in_Extended_and_Narrow, 2)) %>%

write.xlsx(similarities_text_chad_all, "similarities_text_chad_all.xlsx", colNames = TRUE, rowNames=TRUE)
write.xlsx(similarities_text_chad_rel, "similarities_text_chad_rel.xlsx", colNames = TRUE, rowNames=TRUE)
write.xlsx(similarities_headline_chad_extended, "similarities_text_chad_extended.xlsx", colNames = TRUE, rowNames=TRUE)
write.xlsx(similarities_text_chad_narrow, "similarities_text_chad_narrow.xlsx", colNames = TRUE, rowNames=TRUE)
```

Extended search seems to generate articles that include more mentions of more remote (traditionally uncovered) crisis, such as Burundi and South Sudan. There are some countries with less number of articles, such as the DRC, Bangladesh, CAF and Syria. However, the differences are minimal in most cases. 


```{r}
narrow_and_extended <- as.data.frame(intersect(narrow_rel$text, extended_rel$text))
write.xlsx(narrow_and_extended, "narrow_and_extended.xlsx")
narrow_notin_extended <- as.data.frame(setdiff(narrow_rel$text, extended_rel$text))
write.xlsx(narrow_notin_extended, "narrow_notin_extended.xlsx")
extended_notin_narrow <- as.data.frame(setdiff(extended_rel$text, narrow_rel$text))
write.xlsx(extended_notin_narrow, "extended_notin_narrow.xlsx")
```

```{r}
a <- c(1, 2, 3, 4, 6)
b <- c(5, 6, 7, 8, 9)
intersect(a, b)
setdiff(a, b)
setdiff(b, a)
````




are these specific events talked about? - South Asian floods, Iran/Iraq earthquake, Hurrican Irma, Hurricane Harvey, Hurricane Maria

are these specific terms mentioned? Lake Chad, famine, refugee, hurricane
what types of articles are not covered b/n the narrow and extended?
what are the types of articles covered in the first 500 hits?

How many of the articles in the narrow additional to the extended are duplicate?
